### 2021-02-21 math/ia_2021/paper.tex
modif

Regression analysis is a very large portion of statistics, and regression models can 
be found in numerous use cases of the field. Regression models consist of estimating the 
relationship between one (or more) independent variables and a dependent variable. A 
simple example of regression can be seen in the linear relationship between for example

>>>>

Regression analysis is a very large portion of statistics, and regression models can 
be found in numerous use cases of the field. Regression models consist of estimating the 
relationship between one (or more) independent variables and a dependent variable. A 
simple example of regression can be seen in the linear relationship between an independent 
variable $x_{i}$, and the dependent variable $y$. The following expression shows this relationship in what is 
called linear regression, as it models a straight line.

$y = a + \beta x + e $

Where the term $a$ represents the y-intercept of the line and $\beta$ represents the 
coefficient of $x_i$. The final term $e$ is what is known as the error or residual 
term, it is an estimate of the amount by which the predictions differ from the real 
value.

However, the relationship between the distance from an event and the wave height 
is not necessarily linear, especially if it is considered that the travel of 
sound in a fluid obeys the inverse square law. This already tells us a simple 
linear regression model cannot be used for this research. If we want a second degree 
polynomial regression formula, a new $x^2$ term can be added to the previous formula 
and we get:

$y = a + \beta_1 x + \beta_2 x^2 + e$

Even though the right side of this equation is quadratic in $x$, this is still 
linear regression as the right side is linear in $\beta$ (if we were to let 
$x = 1$, we would be left with $y = a + \beta_1 + \beta_2 + e$, which is linear).

In addition, our dataset has two independent variables: the distance from a particular 
earthquake event and the magnitude of that earthquake.

So the relationship between the two independent variables and the wave height can 
be estimated with a multivariate, polynomial regression model. We will use the Python 
scikit-learn library to aid in creating this model.
